\documentclass{article}

\usepackage[preprint,nonatbib]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[british]{babel}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[capitalise,noabbrev]{cleveref}

\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\usepackage{fvextra}

\usepackage{enumitem}
\setlist[itemize]{nosep}
\setlist[enumerate]{nosep}

\frenchspacing

\usepackage{etoc}

\usepackage[backend=biber, style=numeric-comp, natbib=true, sorting=none, backref=true]{biblatex}
\addbibresource{references.bib}

% cleveref: render appendix cross-references as "Appendix N" / "Appendix N.M"
\crefname{appendix}{Appendix}{Appendices}
\Crefname{appendix}{Appendix}{Appendices}
\crefname{subappendix}{Appendix}{Appendices}
\Crefname{subappendix}{Appendix}{Appendices}

% Force pending floats to be placed before each (sub)section starts. Combined
% with placeins (loaded by neurips_2026.sty), this keeps tables and figures
% inside their section: when a float can't fit on the current page it overflows
% to a new page rather than drifting past the next \subsection.
\preto\section{\FloatBarrier}
\preto\subsection{\FloatBarrier}

% Override \backlink (defined in neurips_2026.sty) so each appendix section also
% links back to the appendix table of contents (anchored at \label{app:toc}).
\makeatletter
\renewcommand{\backlink}[1]{%
  \hfill{\small%
    \@ifundefined{r@back:#1}{}{%
      \hyperref[back:#1]{\textuparrow\;\cref*{back:#1},\, p.\,\pageref*{back:#1}}%
      \quad\textbar\quad
    }%
    \hyperref[app:toc]{\textuparrow\;Appendix Table of Contents}%
  }%
}
\makeatother

\graphicspath{{figures/}}

% LTeX helper macros — tell the prose checker which arguments to ignore / treat as dummy text.
\newcommand{\ltexignore}[1]{#1}
\newcommand{\ltexdummy}[1]{#1}
\newcommand{\ltexvoweldummy}[1]{#1}
\newcommand{\ltexhidden}[1]{}

\title{Evaluation framework for rewriting attacks on LLM judges of document quality}

\author{%
  Candidate Number: 1099273 \\
}

\begin{document}

\maketitle

% Tag all TOC entries from here on as 'maintext' so the appendix-only TOC
% (configured at \appendix) can hide them.
\etocdepthtag.toc{maintext}

\begin{abstract}

\end{abstract}

% Summative Outlines 

% Related work either after Intro / after Results 

% (Background; e.g. Theory) 

% Methods (past tense) 

% Study Design (overview) / summary of the study / flash-figure 

% Data 

% Models 

% Validation (i.e. evaluation) 

% Results 

% (Can include data preprocessing) 

% Discussion 

% Main findings (don’t introduce new results; 1 paragraph) 

% Relate to other publications (similar, different, etc) 

% Meaning / Mechanism 

% Limitations 

% Future Directions 

% (Conclusion) 


%Notes
% Avoid 3-level hierarchy 

% No code in Appendix 

% Intro 

% wide shot -> niche -> gap 

% Contributions (bullet points) 

% Related Work 

% Can mention formulas 

% Flash figure: 

% Captions should be self sufficient; things mentioned in figure don’t need to be repeated 

% Models: use multiple to be robust 

% Appendix: what prompts you used, models you explored 

% Results match in parallel to contributions in introduction


\section{Introduction}
\label{sec:intro}

With large language models being widely used to make quality judgements about documents and websites, there is a concern that people who stand to benefit from being positively assessed will seek to game them. LLMs are being integrated into systems which screen resumes and rank search results \citep{sunChatGPTGoodSearch2023}; moreover, when a consumer uses a chatbot to learn about a topical issue, they rely on a LLM to filter hundreds of websites \citep{chatterjiHowPeopleUse2025}. For people \textit{creating} resumes, websites, and political content, there is a clear benefit to being positively assessed by LLMs and highlighted to information seekers. This has given rise to well-funded startups promising to improve the visibility of their clients' websites in LLM responses via `answer engine optimisation' \citep{coffeeBillionDollarQuestionHangs2025}. 

These startups aim to replicate the commercial success of search engine optimisation (SEO), which denotes practices which promote a website's visibility in search engine results. While SEO firms have profited, SEO optimisations have  , SEO has degraded search result quality by fuelling the prominence of spam in search engine results across several query categories, such as product reviews or health \citep{bevendorffGoogleGettingWorse2024a, warzelOpenSecretGoogle2022}. 

The example of SEO raises a question: could `answer engine optimisation' degrade the quality of LLM responses? A necessary step in addressing this question is determining the potential effectiveness \textit{and} harmfulness of optimisation strategies. 

It is worth distinguishing between two distinct types of optimisation methods. In the first, the attacker does not care about preserving the meaning of their content. Prompt-injection attacks fall under this category, and have proven effective at deceiving LLM evaluators into providing high scores for low-quality content \citep{liLLMsCannotReliably2025}. 

In the second type of attack, the attacker cares about preserving the meaning of their content. This will be the case for any situation which involves a combination of LLM and human assessment, such as submitting a paper to a conference. We term such attacks `rewriting attacks', and they are the focus of this study.

Our paper provides a general framework for estimating both the effectiveness and harmfulness of rewriting attacks. This framework is motivated by the following observations: 

\begin{enumerate}
  \item Attack methods should be evaluated as if the attacker does not know what LLM will be used to judge their content.
  \item Novel rewriting attacks should be evaluated in comparison against baseline attack methods.
  \item It is possible for a rewriting attack to be effective, without being harmful, by genuinely improving the quality of a document.
\end{enumerate}

Every existing study of rewriting attacks does not address at least two of these considerations. For example, \citet{kanekoParaphrasingAdversarialAttack2026} estimates the effectiveness of an attack method against a different LLM judge than the one used for training. They estimate a reduced but still positive boost to the content's score, and conclude that it .  in attack effectiveness,  However, they do not consider whether a simpler (or even naive) method 





by these LLM-powered systems. Similarly to search engine optimisation, 



Concern about people optimising their shit (papers, commercial advice on optimisation) - term rewriting attacks

Papers studying rewriting attacks have several deficiencies. 

- Not comparing against a baseline 
- Using the same judges for training and evaluation
- 


We argue that a rewriting attack is only successful, from the attackers' perspective, if it meets the following two requirements:
\begin{itemize}
  \item The rewritten content is rated well by an unknown judge model.
  \item The rewritten content is similar in meaning to the original content.
\end{itemize}
Moreover, we argue that a rewriting attack is only problematic, from the defender's perspective, under the following condition:
\begin{itemize}
  \item The increase in the rewritten content's rating is larger than the increase in the rewritten content's quality.
\end{itemize}

If 
We argue for the practical relevance of these requirements, and show that existing research into rewriting attacks has neglected one or both of them.


\section{Methods}

\subsection{Background}

In a `rewriting attack', the attacker aims to improve how their document is scored by an LLM-as-a-judge, by rewriting the document while preserving its meaning. We formalise this in the following manner. We define $D$ as the space of all possible documents. A rewriter $R : D \to D$ maps an original document $x \in D$ to a rewritten document $R(x) \in D$. 

A semantic similarity function $S : D \times D \to [0,1]$ measures how similar two documents are in meaning. If $S(x,y) = 1$ for two documents $x$ and $y$, then they are identical.

The collection of all possible LLM judges is denoted as $\mathcal{J}$. A judge $J \in \mathcal{J}$ maps a document $x$ to its score $J(x) \in \mathbb{R}$. 

The aim of an attacker is to choose a rewriter $R$ which maximises $J(R(x))$, the judge score of a rewritten document, while maintaining semantic similarity. This optimisation problem may be stated as
\begin{equation}\label{eq:known}
  \text{choose} \ R \  \text{to maximise} \ J(R(x)) \ \text{such that} \ S(x,R(x)) > \epsilon,
\end{equation}
where $\epsilon \in [0,1]$ is a tolerance threshold defining how much semantic drift the attacker is willing to tolerate.

The above formulation of the optimisation problem assumes that the judge $J$ is known or accessible to the attacker. This is not the case in general. To account for uncertainty, we can define a probability distribution $\mu$ over possible judges. This represents the attackers' beliefs about the probability that a given judge model $J$ is being used.

The attacker then aims to maximise the expected score of the rewritten document, after taking this uncertainty into account:
\begin{equation}\label{eq:uncertain}
  \text{choose} \ R \  \text{to maximise} \ \mathbb{E}_\mu[J(R(x))] \ \text{such that} \ S(x,R(x)) > \epsilon.
\end{equation}

Note that if the attacker is completely certain that a specific judge will be used, then \cref{eq:uncertain} simplifies to \cref{eq:known} (see \appref{app:proof} for proof). For this reason, we refer to \cref{eq:known} as the known-judge formulation, and \cref{eq:uncertain} as the unknown-judge formulation. 

We argue that the unknown-judge formulation is almost always the more appropriate formulation to evaluate rewriting attacks, and devise an approximation to operationalise it.

\paragraph{Harmfulness of rewriting attacks}
The goal of a LLM-as-a-judge system is to accurately estimate quality. If we denote $Q : D \to \mathbb{R}$ as the true quality of a document, then this goal can be written in the following manner,
\begin{equation}
  \text{minimise } \mathbb{E}[(Q(x) - J(x))^2],
\end{equation}
after defining some suitability probability distribution over possible input documents.

There is a notable asymmetry between the goals of the attacker and defender. The attacker wants high scores from the LLM judge; the defender wants accurate scores. If the rewriter $R$ increases document quality, and the LLM-as-a-judge $J$ maintains its accuracy on rewritten documents, then both attacker and defender achieve their goals. Such a situation is beneficial to the `attacker' without posing harms to the `defender'. 

\subsection{Attack methods}

\paragraph{Data}

We use a filtered corpus of documents from \citet{rottgerQuantifyingDistortiveImpacts2025} for our experiments. The full corpus consists of 10008 documents written in response to 100 UK-related political propositions, such as ``The UK should increase taxes on sugary drinks." Half the documents were written by humans selected from a Prolific UK representative sample, and half were written by LLMs. We select human responses to the 40 most controversial topics, yielding 1805 documents. We split these 60/40 into a training dataset ($n=1091$) and an evaluation dataset ($n=714$) using a stratified sampling strategy to ensure balance across propositions (see \appref{app:corpus} for details). All reported evaluation metrics are recorded using this evaluation dataset.

\paragraph{Attack method characteristics}

We test five attack methods. They span two axes: whether the method requires feedback from a judge during use (\emph{judge-in-the-loop} vs \emph{judge-free}), and whether it requires finetuning the rewriter (\emph{finetuning} vs \emph{prompt-only}). 

\paragraph{Prompt-only and judge-free} We test two rewriting methods. The first, `naive', prompts the rewriter to rewrite the paragraph while preserving stance and approximate word count. The second, `literature-informed', instructs the judge to rewrite the paragraph while applying writing principles that have been found to improve LLM assessments of document quality in previous studies \citep{aggarwalGEOGenerativeEngine2024a, liuGEvalNLGEvaluation2023, kimPrometheusInducingFineGrained2023}.

\paragraph{Prompt-only and judge-in-the-loop} We implement a Best-of-N approach, in which 16 rewrites are generated using the literature-informed prompt, and then a single rewrite is selected, based on feedback from one or more judges chosen by the attacker. We use 

\paragraph{Finetuning and judge-in-the-loop}

\subsection{Operationalising evaluation criteria}
\label{sec:operationalisation}

\paragraph{Estimating semantic similarity}

To measure whether rewritten documents preserve the meaning, or semantics, of the original document, we used a natural language inference (NLI) model \citep{bowmanLargeAnnotatedCorpus2015}. A NLI model $NLI : D \times D$ takes two documents $x$ and $y$ as input and returns a score $NLI(x,y) \in [0,1]$ which measures whether $x$ `entails' $y$. For an example of entailment, `National parks protect beautiful landscapes.' entails `Beautiful landscapes are protected by national parks.', but does not entail `National parks are good for local economies.'

While there are nuances to the exact definition of entailment, NLI models have proven practically effective at preserving the meaning of documents in paragraphing or rewriting tasks, outperforming alternatives such as embedding cosine similarity \citep{babakovLargescaleComputationalStudy2022}. We adopt the Mutual Implication Score (MIS) from \citep{babakovLargescaleComputationalStudy2022} as our measure of semantic similarity. It averages forward and backward entailment between the original and re-written documents,
\begin{equation}
  \text{MIS}(x,R(x)) = \frac{1}{2} (NLI(x,R(x)) + NLI(R(x),x)).
\end{equation}
We used the ModernBERT-large-zeroshot-v2.0 NLI model (\href{https://huggingface.co/MoritzLaurer/ModernBERT-large-zeroshot-v2.0}{Hugging Face repository}). This model almost achieves SOTA accuracy on NLI benchmarks, meets our context length requirements, and is faster than alternatives \citep{laurerBuildingEfficientUniversal2024}. To aid interpretation, we provide examples of MIS scores in \appref{app:nli-examples}. In line with existing literature, we also confirm that embedding similarity is insufficient to measure semantic fidelity.

\paragraph{Estimating known-judge effectiveness}

Several of the attack methods described use judge models for feedback, which we refer to as `known' judge models from here on. We used the known judge models to estimate known-judge effectiveness in the following way. 

For judge-agnostic attack methods, we calculate the average of all three judge scores. For judge-in-the-loop attack methods, we calculate the average scores of the judge(s) used for feedback.




\begin{equation}
  \text{Known-judge effectiveness} := \frac{1}{M} \sum_{i=1}^M \frac{1}{|F_i|}\sum_{j \in F_i} J(x)
\end{equation}

\paragraph{Estimating unknown-judge effectiveness}

To estimate 

\paragraph{Comparing the scores of different LLMs}

To compare between the scores of in-sample 

\paragraph{Estimating true document quality}

While it might be possible to approximate $Q$ by using human labellers, we lacked the resources to do so for this study. Instead, we used a panel of `high-capability' judges. We use . These are the models 

\subsection{Experimental setup}
\label{sec:exp-setup}

\paragraph{Judge models and folds}
We use a 3-fold leave-one-out (LOO) protocol over three in-training judges: Qwen-2.5-9B (\texttt{Qwen/Qwen2.5-9B}), Llama-3.1-8B-Instruct (\texttt{meta-llama/Llama-3.1-8B-Instruct}), and Gemma-2-9B-it (\texttt{google/gemma-2-9b-it}). Within each fold, two of these judges are used both for any judge-in-the-loop method (BoN candidate scoring, GRPO reward) and for in-sample evaluation; the third is held out as a near-domain transfer judge. The rotation is: fold~1 trains on Qwen and Llama, fold~2 on Qwen and Gemma, fold~3 on Llama and Gemma. In addition to the LOO held-out judge, we evaluate every method on three fully out-of-sample judges that are not used at any stage of method development: Mistral-7B-Instruct-v0.3 (\texttt{mistralai/Mistral-7B-Instruct-v0.3}), Phi-3.5-mini-instruct (\texttt{microsoft/Phi-3.5-mini-instruct}), and Command-R-7B (\texttt{CohereLabs/c4ai-command-r7b-12-2024}). The out-of-sample judges are drawn from different families and providers than the in-training judges, but at comparable scale, so any cross-judge gap reflects family or provider transfer rather than scale. All judge inference uses vLLM with bfloat16 weights, deterministic decoding (temperature 0), and identical prompts across all judges (\appref{app:judge-prompts}).

\paragraph{Rewriter models}
For prompt-only methods and BoN, we use Qwen-2.5-1.5B-Instruct (\texttt{Qwen/Qwen2.5-1.5B-Instruct}) as the rewriter base. For GRPO, we train three rewriter bases independently: Qwen-2.5-1.5B-Instruct, LFM2.5-1.2B-Instruct (\texttt{LiquidAI/LFM2.5-1.2B-Instruct}), and Gemma-3-1B-it (\texttt{google/gemma-3-1b-it}). Prompt-only rewriters and BoN candidates sample at temperature 0.7; GRPO rollouts at temperature 1.0.

\paragraph{Criteria}
Each rewrite is evaluated on two criteria, \emph{clarity} and \emph{informativeness}, scored on a 0--100 scale by every judge. Clarity targets prose quality (grammar, sentence structure, logical flow, first-read comprehensibility); informativeness targets substantive content (specific facts, mechanisms, explicit reasoning, appropriate hedging). The judge rubrics explicitly disentangle the two criteria: the clarity rubric instructs the judge not to reward informational content, and the informativeness rubric instructs the judge not to reward grammar or prose quality. Full rubrics are in \appref{app:judge-prompts}.

\paragraph{Compute}
All training and inference is run on a single NVIDIA A100 80\,GB GPU. A 400-step GRPO run takes roughly 90--120 minutes; the full panel (3 rewriter bases $\times$ 2 criteria $\times$ 3 folds $\times$ 2 fidelity variants $=$ 36 configurations) is run sequentially.

\subsection{Experimental design}
\label{sec:exp-design}

The setup above is designed to answer three questions in parallel.
\begin{enumerate}
  \item \emph{Does feeding back an ensemble of two judges, rather than a single judge, narrow the in-sample/out-of-sample gap?} The 3-fold LOO protocol gives within-fold paired comparisons for every method, and the contrast between the LOO held-out judge and the three fully out-of-sample judges separates near-domain transfer from far-domain transfer.
  \item \emph{Does NLI-based fidelity outperform embedding-similarity fidelity at preserving meaning while still admitting effective rewrites?} The two GRPO variants are matched on every other hyperparameter, isolating the choice of fidelity term.
  \item \emph{What proportion of each method's measured uplift is attributable to genuine quality improvement, rather than judge-specific gaming?} The regression in \appref{app:regression} decomposes the ADD per method into in-sample and out-of-sample components, contrasted with the semantic-fidelity scores from both metrics.
\end{enumerate}



\section{Results}

differential effectiveness of boost across political spectrum?

or just dragging across political spectrum - might be simpler?

\paragraph{Comparing }

\paragraph{Semantic fidelity and unknown-judge performance across methods}

\paragraph{Comparing embedding similarity and NLI model performance}

\paragraph{Measuring harmfulness across }

\paragraph{After preserving strict semantic fidelity, harmfulness of attack methods is minimal????????}


\section{Discussion}

In the space of rewriting attacks on LLM-as-a-judge, there are several common gaps:
1. Comparing against a baseline model
2. Measuring whether attacks are successful against a held-out judge
3. Realistic measures of semantic drift
4. Distinguishing what proportion of attack efficacy is due to genuine improvement
5. Cost and ease (both in terms of inference and development)

These considerations have important consequences
1. A complicated or costly method might underperform relative to a simple baseline. For example, simply being AI-written can improve content.
2. In general, an attacker will not know what model is being used as a judge. If methods fail to generalise - or *differentially* generalise - it might shift the relative performance of attack methods. 
3. Attacks commonly used methods such as embedding cosine similarity or KL-divergence as guardrails or regularisation in loss functions to control semantic drift. However, there is typically no systematic measurement of whether attack methods introduce semantic drift.
4. ``Attacks'' on LLM-as-a-judge might just represent genuine improvement. Few papers addressing attacks on LLM-as-a-judge address this question.  While in a distinguishing between genuine quality improvements and 

Depends on whether people or organisations want to do this at scale (in which case inference cost is important, up-front cost or complexity is not important), or if people want to do this themselves

% Research into the efficacy of attack methods ought to be framed according to their goal. Do they aim to demonstrate:
% a) What is scientifically possible?
% b) What is practically relevant?

We develop an evaluation framework which, for a given attack method, estimates a) its effectiveness when the judge LLM is unknown, b) what proportion of the attack success is due to genuine improvement in quality, and c) the extent of semantic drift

We apply this evaluation to two panels of attack methods. The first is a range of attack methods (including both training-free and training-intensive) methods, all using the same base model. We thus compare attack methods across the criteria mentioned above, holding the underlying capability of the model constant.

For the second panel, we compare training-free attack methods across increasing scales. Training-free methods are much easier to implement and serve, and can take advantage of improved model capabilities immediately. Hence, this panel investigates whether increasing scale (and underlying capabilities of models) produces gains along our evaluation criteria.

\printbibliography

\appendix
% After \appendix, treat sections/subsections as appendices for cleveref naming
\crefalias{section}{appendix}
\crefalias{subsection}{subappendix}

% Mark entries written from now on with the 'appendix' tag
\etocdepthtag.toc{appendix}

% Hide main-text entries; show appendix sections + subsections only
\etocsettagdepth{maintext}{none}
\etocsettagdepth{appendix}{subsection}

% Appendix opener: page break, title, and clickable appendix-only ToC
\newpage
\phantomsection\label{app:toc}
\section*{Appendix}
\tableofcontents

\include{appendix}

\end{document}
